%%% Research Diary - Entry
\documentclass[11pt,letterpaper]{article}

% Working date: The date this entry is describing. Not necessary the date of last edit.
\newcommand{\workingDate}{\textsc{  2012 $|$ 1 $|$ 16 } }

% Name and institution must preceed call to researchdiary.sty package
\newcommand{\userName}{ BW Keller }
\newcommand{\institution}{ McMaster University }

% The guts and glory
\usepackage{research_diary}
\setcounter{secnumdepth}{-1}

% Begin document
\begin{document}

\section{To Do}
\begin{bullets}
\item[\checkmark] Replicate figure 5 from Hopkins 2011
\item[\checkmark] Run ionization test cases
\item Track down cause of ChaNGa crash at time \~0.3
\end{bullets}

\textleaf : \textit{In Progress} \qquad \checkmark : \textit{Completed}
\section{Daily Log}

\subsection{Monday}

Over the weekend I received and email from Greg suggesting I remove the
\texttt{-DRTF} flag from gasoline to speed up the running (specifically
the problem with ;arge values of \texttt{iRung}.) This worked, and James
suggested I try running with the \texttt{-DRTFORCE} enabled.

\subsection{Tuesday}

I've started a test of Greg's IC with the \texttt{-DRTFORCE}. We shall
see if it is slow or not soon. I'm also going to finish reproducing the
Hopkins figure, using \texttt{Research/code/scripts/mass\_inflow.py}.
I've copied all the mass inflow code I've been playing with to
\texttt{Research/code/scripts/mass\_inflow\_test.py}. It looks like I
may need to do some more playing, as there is some issue with
reproducing the values of \texttt{dM/dt} that are found in Hopkins
figure 1. I think this may be due to the low age of the galaxy. We'll
see what happens if I evolve it further.

\subsection{Thursday}

Today was a very productive day. We had a group meeting early, at 10AM,
in which I showed off the pynmovies I made. After lunch, I met with
James and we discussed the direction my work will be going in coming
months, with a focus on a potential paper extending Cameron Hummels work
on suppression of star formation through metal cooling. What James wants
to do is produce a comparison of three runs, all with cosmological
initial conditions: one with just metal cooling, one with metal cooling
plus Rayleigh-Taylor subgrid modelling, and one with RT forces and the
ionization feedback. James hopes this will let us produce a paper in
just a few months. I believe he suggested we use Greg's g1536 initial
conditions as a starting point to run these test cases. James also sent
me a new IC of a simple MW-type galaxy. I've stored it at
\texttt{Research/data/isol\_galaxy} on fox2, and I am running a version
of it with and without ionization. James also wanted to take a look at
starformation rates, so I've written a tool to read and plot data from
the XDR-formatted starlog files that gasoline produces. This tool is at
\texttt{Research/code/scripts/starlog.py}. I'll be extending it as time
allows.

\subsection{Friday}

James and I found (and subsequently fixed) a major bug in gasoline where
it was not actually ionizing and heating the gas around a new star, but
the star particle itself. I've restarted all the jobs that were affected
by this with the fixed version of gasoline. James also suggested I
generate some plots to examine the results: one of a temperature
histogram (particles in T bins), and one of $\log T$ vs $\log\rho$ to
see if the gas chunks are actually getting ionized. I've also organized
my files on orca a bit more. Here's where the runs are all currently
stored: * \texttt{/work/kellerbw/g1536\_noionize\_DRTFORCE}

\begin{verbatim}
Greg's g1536 ICs, run with
UV ionization disabled, and using the RTFORCE RT subgrid flag on.  Metal cooling
is used here too.
\end{verbatim}

\begin{itemize}
\item
  \texttt{/work/kellerbw/g1536\_ionize\_DRTFORCE} Greg's g1536 ICs, run
  with UV ionization enabled, and using the RTFORCE RT subgrid flag on.
  Metal cooling is used here too.
\item
  \texttt{/work/kellerbw/isol\_galaxy\_ionization\_DRTFORCE}\} James'
  simple galaxy IC, run with UV ionization enabled, and using the
  RTFORCE RT subgrid flag on. Metal cooling is used here too.
\item
  \texttt{/work/kellerbw/isol\_galaxy\_noionization\_DRTFORCE}\} James'
  simple galaxy IC, run with UV ionization disabled, and using the
  RTFORCE RT subgrid flag on. Metal cooling is used here too.
\item
  \texttt{/work/kellerbw/Tom\_IC\_ionization\_DRTFORCE}\} Tom's ICs, run
  with UV ionization enabled, and using the RTFORCE RT subgrid flag on.
  Metal cooling is used here too.
\item
  \texttt{/work/kellerbw/Tom\_IC\_noionization\_DRTFORCE}\} Tom's ICs,
  run with UV ionization disabled, and using the RTFORCE RT subgrid flag
  on. Metal cooling is used here too.
\end{itemize}

I've also tarballed up some older runs that may not be of use in the
future: * \texttt{/work/kellerbw/Tom\_IC\_1strun.tar.gz} The first
successful full run of Tom's ICs. This may be crap, as I ran it with
cosmological cooling, rather than metal cooling. Also, UV background is
off.

\begin{itemize}
\item
  \texttt{/work/kellerbw/Tom\_IC\_1strun\_moresteps.tar.gz}\} The same
  as above, but with tipsy outputs every 1 timesteps instead of every
  10.
\item
  \texttt{/work/kellerbw/Tom\_IC\_noionization\_DRTF.tar.gz}\} The same
  as \texttt{Tom\_IC\_noionization\_DRTFORCE}, but with the
  \texttt{-DRTF} flag instead of \texttt{-DRTFORCE}. This flag totally
  shits the bed in some density edge situations, so I don't think we
  will be using it in the future.
\end{itemize}


\end{document}