%%% Research Diary - Entry
\documentclass[11pt,letterpaper]{article}

% Working date: The date this entry is describing. Not necessary the date of last edit.
\newcommand{\workingDate}{\textsc{  2012 $|$ 1 $|$ 23 } }

% Name and institution must preceed call to researchdiary.sty package
\newcommand{\userName}{ BW Keller }
\newcommand{\institution}{ McMaster University }

% The guts and glory
\usepackage{research_diary}
\setcounter{secnumdepth}{-1}

% Begin document
\begin{document}

\section{To Do}
\begin{bullets}
\item[\textleaf] Replicate figure 5 from Hopkins 2011
\item Track down cause of ChaNGa crash at time 0.3
\end{bullets}

\textleaf : \textit{In Progress} \qquad \checkmark : \textit{Completed}
\section{Daily Log}

\subsection{Wednesday}

I have come to the unfortunate realization that gasoline's checkpointing
behaves poorly with the \verb!.log! and \verb!.starlog! files, as in it
just gives up writing to them if there is a file already there. Ugh. So,
all of my ``resumed'' jobs are lacking starformation history files. I
have restarted Tom's ICs for the non-ionized part, because the starlog
was broken. It looks like gasoline is \textit{supposed} to resume things
gracefully, but I guess something on orca crapped out again. This is
particulary weird, because g1536 has restarted fine a number of times.
So the status with my current simulations are:

\begin{itemize}
\item
  \verb!/work/kellerbw/g1536_noionize_DRTFORCE!\} Still running, iRung
  is going crazy again though
\item
  \verb!/work/kellerbw/g1536_ionize_DRTFORCE!\} Still running, iRung is
  going crazy again though
\item
  \verb!/work/kellerbw/isol_galaxy_ionization_DRTFORCE!\checkmark\}
  Finished, copied to fox2, but the starformation rate is so low (or
  resolution is too coarse) to see any big difference in the SFR without
  ionization
\item
  \verb!/work/kellerbw/isol_galaxy_noionization_DRTFORCE!\checkmark\}i
  See above
\item
  \verb!/work/kellerbw/Tom_IC_ionization_DRTFORCE!\checkmark\} Looks
  good, needs to run longer. I've set it up for 400 steps, instead of
  the previous 150.
\item
  \verb!/work/kellerbw/Tom_IC_noionization_DRTFORCE!\} The log and
  starlog are totally wrecked. I've restarted from the beginning, but
  orca is being difficult today, so it may take a while
\end{itemize}

James suggested examining a density versus temperature phase diagram as
a way of comparing runs.


\end{document}