%%% Research Diary - Entry
\documentclass[11pt,letterpaper]{article}

% Working date: The date this entry is describing. Not necessary the date of last edit.
\newcommand{\workingDate}{\textsc{  2012 $|$ 1 $|$  9 } }

% Name and institution must preceed call to researchdiary.sty package
\newcommand{\userName}{ BW Keller }
\newcommand{\institution}{ McMaster University }

% The guts and glory
\usepackage{research_diary}
\setcounter{secnumdepth}{-1}

% Begin document
\begin{document}

\section{To Do}
\begin{bullets}
\item[\checkmark] Run Tom's ICs on gasoline.
\item[\textleaf] Replicate figure 5 from Hopkins 2011
\item[\checkmark] Make some cool movies using pynbody
\item[\textleaf] Run ionization test cases
\item Track down cause of ChaNGa crash at time \~0.3
\end{bullets}

\textleaf : \textit{In Progress} \qquad \checkmark : \textit{Completed}
\section{Daily Log}

\subsection{Monday}

I've begun working on the mass inflow calculator in earnest in
\verb!Research/code/scripts/mass_inflow.py! using the algorithm James
and I discussed Friday. It will calculate the mass flow through a shell
with inner radius $R$ and outer radius $R+\Delta R$

\subsection{Wednesday}

I've finished up fiddling with pynbody and the mass inflow calculator,
and I feel sufficiently confident that I can now reproduce figure 5 from
Hopkins 2011. \textbackslash{} I've just had an extremely eventful and
productive meeting with James and Greg Stinson. We've implemented a new
feature in gasoline, a copy of which can be found at
\verb!Research/code/gasoline_ionization!. What the new code does is that
after each star formation event, we simulate the effects of UV
ionization on the surrounding gas by heating it to 8000 K, and turning
off the cooling features (as ionized HII cools inefficiently). This has
the effect of a de facto starformation killer, and will moderate the
starformation rate in an area not by removing gas, but by raising its
temperature above the starformation threshold of 1000 K (simply change
dTempMax in the parameter file).\\This will also have an effect on SN
feedback. I need to run the new code on an initial condition Greg will
send me, and on Tom's ICs after the initial burst in starformation is
over. I need to plot that to find out when it is! I will also need to
run this with the original gasoline as a comparison to see what the
effect of the new physics is. I've emailed Greg about sending me the
location for his initial conditions. I will need to run this with metal
cooling. I also need to add the \verb!-DDIFFUSION! flag to the
compile-time options. I also need to remember to copy the
\verb!cooltable_xdr! to the working directory of any run that uses the
metal cooling.

\subsection{Friday}

I began to feel a bit over my head today. Yesterday afternoon, I met
with Greg, and we found that gasoline was running his \verb!g1536!
intial conditions very slowly, and this was due to \verb!iRung! being
knocked up to large ($\approx15$) values after the completion of the
first timestep. I was unable to find the cause of this. I've started a
run of Greg's ICs with checkpointing fixed, and with tipsy outputs at
every timestep. I've restarted all of the ionization comparison runs,
and James advised me to keep code and data separate, with code in
\verb!~kellerbw! and data on \verb!/work/kellerbw!. Once the comparison
runs are complete, I will reorganize my data on SHARCNet.


\end{document}