%%% Research Diary - Entry
\documentclass[11pt,letterpaper]{article}

% Working date: The date this entry is describing. Not necessary the date of last edit.
\newcommand{\workingDate}{\textsc{  2012 $|$ 9 $|$ 17 } }

% Name and institution must preceed call to researchdiary.sty package
\newcommand{\userName}{ BW Keller }
\newcommand{\institution}{ McMaster University }

% The guts and glory
\usepackage{research_diary}
\setcounter{secnumdepth}{-1}

% Begin document
\begin{document}

\section{To Do}
\begin{bullets}
\item[\textleaf] Run disk comparison - basic test
\item[\textleaf] Rerun MAGICC onestar with no cooling (bGasAdiabatic)
\item Give Greg debug information
\item[\checkmark] Symposium day talk.
\item Read Behroozi paper
\item[\textleaf] Re-run Chris IC with DRTFORCE
\item[\checkmark] Make Isotropic onestar box.
\item Fix onestar box timesteps
\item Get phase plots of the g1536 galaxy
\end{bullets}

\textleaf : \textit{In Progress} \qquad \checkmark : \textit{Completed}
\subsection{Daily Log}

\section{Tuesday}

I had a lunch meeting with James today. He is very keen on getting a
simple, working ESF model to start playing with. We don't need much in
the way of the underlying physical principle. Once we have this, we can
do a HUGE galaxy run ($10 \Msun$ particles).

I spent the afternoon helping James get familiar with git and merge his
copy of gasoline to the latest version from UW. I also created a syntax
highlighting file for lanyon entries, so that these journal entries will
look pretty and clean in vim.

\section{Wednesday}

I am \textbf{finally} getting back to work after a long two weeks of
summer school and the symposium day talk.

I'm going to try and get to the bottom of why our ESF isn't working as
well as MAGICC. I have a few ideas:

\begin{itemize}
\item
  Not enough energy being input (\textbf{I Think this is it!})
\item
  HII regions saturating the disk, preventing new ionization
  (\textbf{not the answer, the fraction of mgot/mwanted averaged for
  1000 steps is 1 to 6 decimal places})
\item
  SNe and ESF doing effectively the same thing, so I'm just changing the
  timing
\end{itemize}

In order to fully test this, I need that isotropic onestar box. I'm
going to make one with a uniform temperature of 1000K. The positions
will be random, but isotropic to give a cube of 1 code unit per side. I
should probably make the conditions inside similar to my SF threshold
(10 atom/cc).

After examining the result of the single star ionization run, it looks
like a very small amount of energy is being injected. At 10 atom/cc and
1000K, the additional energy put into the box is a mere \$ 10\^{}\{46\}
erg/Msun\$. This explains everything. The additional temperature is not
enough to actually drive a wind or lift anything, and so the disk
collapses further just like in the low SFE examples from Aquila. All the
Ionizing feedback is doing is pushing the star formation backwards by
the dIonizeTime.

Tomorrow I want to hack together a simple ESF routine, a la SB99.

\section{Thursday}


\end{document}