%%% Research Diary - Entry
\documentclass[11pt,letterpaper]{article}

% Working date: The date this entry is describing. Not necessary the date of last edit.
\newcommand{\workingDate}{\textsc{  2012 $|$ 5 $|$ 28 } }

% Name and institution must preceed call to researchdiary.sty package
\newcommand{\userName}{ BW Keller }
\newcommand{\institution}{ McMaster University }

% The guts and glory
\usepackage{research_diary}
\setcounter{secnumdepth}{-1}

% Begin document
\begin{document}

\section{To Do}
\begin{bullets}
\item[\checkmark] Add Chris' potential to gasoline
\item[\checkmark] Run Chris' Disk adiabatically
\item[\checkmark] Run Chris' Disk with fabiogal parameter
\item[\textleaf] CASCA Poster
\end{bullets}

\textleaf : \textit{In Progress} \qquad \checkmark : \textit{Completed}
\section{Daily Log}

\subsection{Monday}

Once James returned last week, we were able to solve the problem of self
gravitation in Chris' parameters: it turns out that gasoline's gravity
solver is broken for noncubic periodic volumes. We've hacked a fix for
this by setting in the parameter file:

\begin{verbatim}
bEwald = 0
nReplicas = 5
dxPeriod = 1
dyPeriod = 1
dzPeriod = 0
\end{verbatim}

I met with James today after searching through the Thode for

\subsection{Tuesday}

I tried running the volume with \texttt{dPhysDenMin=1}, 10 times higher
than the default value Fabio used. It didn't make any appreciable
difference, changing the average SFR from 0.04285 to 0.04283 (a 0.05
percent change). I'm going to try increasing it by an order of
magnitude, to 10 atoms/cc. WAIT: I think that may not work, since
\texttt{dOverDenMin} is also used, it might override that setting. I've
removed it from the file, so we will see how that goes now with the same
other settings as before.

I really would like to get myself a queue system for angband so that I
could just pile jobs up and have it email me when they finish or die. I
may have to write my own.

I just got a message from James. Apparently some of the occassional
crashes I was having in my starforming runs was because I need to
inclode the parameter \texttt{dExtraStore=a} where $a>0.6$. Obviously.


\end{document}