%%% Research Diary - Entry
\documentclass[11pt,letterpaper]{article}

% Working date: The date this entry is describing. Not necessary the date of last edit.
\newcommand{\workingDate}{\textsc{  2012 $|$ 2 $|$  6 } }

% Name and institution must preceed call to researchdiary.sty package
\newcommand{\userName}{ BW Keller }
\newcommand{\institution}{ McMaster University }

% The guts and glory
\usepackage{research_diary}
\setcounter{secnumdepth}{-1}

% Begin document
\begin{document}

\section{To Do}
\begin{bullets}
\item[\checkmark] Figure out if the stellar gas ionization is actually affecting SFR
\item[\checkmark] Replicate figure 5 from Hopkins 2011
\item \sout{Track down cause of ChaNGa crash at time 0.3}
\item Get to the bottom of the rung issue with the RTFORCE
\end{bullets}

\textleaf : \textit{In Progress} \qquad \checkmark : \textit{Completed}
\section{Daily Log}

\subsection{Tuesday}

I had a discussion with James today showing him the $\rho$ vs. $T$ delta
diagram I produced, as well as the SFR vs.~time plot for Tom's ICs run
to test the new ionization hack we added (they show that the SFR is not
suppressed).\\James thinks that the hack may not be suppressing SFR
because of resolution issues (we aren't resolving clusters of star
formation). James will send me a higher resolution IC soon to test this
hypothesis with. He also suggested using a simple periodic box, but I
will need to learn how to set that up.

\subsection{Wednesday}

I received an email from James yesterday asking about the RTF/RTFORCE
rung issue. He wants to understand the origin of the small steps. He
said that what we need is a single output with many rungs that we can
compare RTF and RTFORCE. James thinks that the cause of the rung issue
is the result of evolution. The cause could be one of the following:

\begin{itemize}
\item
  Very high density (small smoothing h) $dt \approx h/c$
\item
  Very high temperatures (large c) $dt \approx h/c$
\item
  Very high accelerations $dt \approx \sqrt{\epsilon/a}$
\item
  Very rapid cooling $dt \approx E/\dot E$
\item
  Very large convergent velocities $dt \approx h/|dv|, dv < 0$
\end{itemize}

In order to test this, James has asked me to run a param file with
nSteps=0 using an intermediate output for the IC. This will produce of a
dump of many properties, most importantly dt for all the particles.
James wants to see a plot of $dt$ vs $\rho$ for the following versions
of Greg's ICs until the iRung blows up, and the different executables
for each of these are at (on orca):

\begin{itemize}
\item
  \emph{DRTFORCE}

  \texttt{\textasciitilde{}/gasoline\_ionization/gasoline.DRTFORCE}
\item
  \emph{DRTF}

  \texttt{\textasciitilde{}/gasoline\_ionization/gasoline.DRTF}
\item
  \emph{Neither DRTF or DRTFORCE}

  \texttt{\textasciitilde{}/gasoline\_ionization/gasoline.NORT}
\end{itemize}

I've stored each of these runs in a directory corresponding to the
executable suffix at \texttt{/work/kellerbw/iRung\_Test/} on orca.


\end{document}