%%% Research Diary - Entry
\documentclass[11pt,letterpaper]{article}

% Working date: The date this entry is describing. Not necessary the date of last edit.
\newcommand{\workingDate}{\textsc{  2012 $|$ 4 $|$ 24 } }

% Name and institution must preceed call to researchdiary.sty package
\newcommand{\userName}{ BW Keller }
\newcommand{\institution}{ McMaster University }

% The guts and glory
\usepackage{research_diary}
\setcounter{secnumdepth}{-1}

% Begin document
\begin{document}

\section{To Do}
\begin{bullets}
\item[\checkmark] Rewrite Chris' density profile code to generate SPH ICs
\item[\checkmark] Generate Tipsy file from Chris' IC
\item Add Chris' potential to gasoline's pstGravExternal
\item Run Chris' Disk adiabatically
\item Run Chris' Disk with fabiogal parameter
\end{bullets}

\textleaf : \textit{In Progress} \qquad \checkmark : \textit{Completed}
\section{Ultimate Goal}

Produce realistic (physically accurate) Starformation histories and
rates in Milky-Way type galaxy simulations. This means that their
feedback properties and their SFR/SF histories must match observations.
These observations can be found in Leroy et al. 2008, Walter 2008 (the
THINGS paper), Kennicutt 2008, etc.

\subsection{How to accomplish this}

I am trying to tackle the problem of overcooling and hyperactive
starformation by incorporating more/better physics into the SPH
simulation code. These are either improvements on the existing subgrid
physics (to better match the physical conditions of the galaxy) or to
add new physics (some process that is either unresolved, or is more than
just gravity+hydro). As of today, I have three main prongs that I will
be using to try and achieve my goal

\begin{itemize}
\item
  \emph{RT Force} This is an implementation of the Ritchie and Thomas
  multiphase SPH described in Ritchie \& Thomas 2001. James has already
  written this into gasoline, but I will be testing it out extensively.
  The hope is that this technique will somehow improve the SFR in
  galaxies because of its better handling of fluids made of particles
  with different densities
\item
  \emph{Simple UV Ionization} Elizabeth Harper-Clark's Thesis describes
  the disruption of starforming regions by the clusters they form. She
  found an empirical relation between the amount of stellar mass a Giant
  Molecular Cloud needs to form in order to ionize itself and disrupt
  star formation in it of roughly 7:1 gas:star mass. James and I banged
  together a really quick implementation of this in gasoline, and it
  just heats up neighbours of a newly formed star to 10,000K and turns
  off their cooling for a while. Hopefully this will kill off
  starformation by obliterating clouds that form a lot of stars. We will
  need decent resolution, though, so that the GMCs can actually have a
  reasonable number of particles in them.
\item
  \emph{Hopkins BH Accretion} Gasoline already has some support for sink
  particles. I'm going to add the accretion model from Hopkins 2008 to
  gasoline, and do some simulations of galaxies with SMBH sink particles
  using this better accretion. Hopefully this will give us some feedback
  (How?) that will suppress starformation.
\end{itemize}

\section{Daily Log}

\subsection{Wednesday}

Today I finished the first draft of the poster abstract for CASCA. I've
also transcribed my research road map and downloaded some background
reading.

\subsection{Friday}

Today I \emph{really} got Chris' IC particles finished. I needed to
correct a number of bugs. First and foremost, I forgot that the the
distribution function will automatically try to stretch the z-dimension
to its appropriate size, so I didn't need to make a non-cubic glass to
seed the thing. I've also made separate top and bottom halves, because
the reflection way I was doing it previously was a bad idea. I just
``glue'' the top and bottom slices together by catting them into a
common file. My next goal is to turn the ascii ICs into a tipsy file.

Finished making a tipsy file of the
ICs\texttt{The script}mktipsy.py\texttt{takes the ascii IC position and temperature values and generates initial  conditons.  All this stuff is in}Research/code/chris\_IC`

I need to also implement an additional external potential into gasoline
to capture the potential that Chris is using. Without it, his ICs will
blow up. James suggested I start using the \texttt{pkdBodyForce} in
\texttt{pkd.c} and modify it to fit with Chris' potential. Once this is
done, we will be able to actually run the IC. As a first test, James
wants me to run it adiabatically (no cooling or starformation). If it is
working, it should just sit happily and not really evolve. Once this is
working, we will want to run it using the fabiogal parameter file I
placed in \texttt{Research/code/chris\_IC}. I have some nice clear
objectives for the immediate future. Excellent.


\end{document}