%%% Research Diary - Entry
\documentclass[11pt,letterpaper]{article}

% Working date: The date this entry is describing. Not necessary the date of last edit.
\newcommand{\workingDate}{\textsc{2012 $|$ July $|$ 09}}

% Name and institution must preceed call to researchdiary.sty package
\newcommand{\userName}{Ben Keller}
\newcommand{\institution}{McMaster University}

% The guts and glory
\usepackage{researchdiary}

% Begin document
\begin{document}

\subsection*{To Do}
\begin{bullets} 
\item \checkmark Get phase diagram for ionization run at $\approx 100$ Myr
\item \textleaf Re-run EVERYTHING without divv, and with proper initial star masses
\item \textleaf Run with ionization, no SN
\item Run with 4 glommed together versions of the IC (in the x-y plane)
\end{bullets}

\textleaf : \textit{In Progress} \qquad \checkmark : \textit{Completed}

\section*{Daily Log}
\subsection*{Monday}
I got into the IMPRS summer school!  w00t.  I'll need to see what to do about
funding and lodging.

I keep having a cache miss assertion failing in \verb!mdl.c!.  This is highly
inconvenient, since it makes me have to run on a single core, which is very 
slow.  I'm going to make a debug fork for gasoline to try and hunt this down.

The line causing the bug in the pthread implementation is 
\verb!mdl/pthread/mdl.c:1277!.  It appears to only occur in cases where the 
number of threads is $>1$.  Whelp, if I simply read the damn twiki 
documentation, I would see that this is a common bug, and can be fixed by
editing \verb!MDL_CACHE_SIZE! in mdl.h . I changed it from $2*10^6$ to $3*10^6$.
This didn't seem to work, but it may have been because make spotless doesn't 
remove the \verb!mdl.o! object.  I've also knocked the value up to $4*10^6$.
It still hasn't solved the problem.  I am afeared that this may be due to
the checkpointing again.  I will try and start up a second process, and see
if they fail again.  And just to be nuts, I'm going to knock the cache up to 8
million.
\end{document}
