%%% Research Diary - Entry
\documentclass[11pt,letterpaper]{article}

% Working date: The date this entry is describing. Not necessary the date of last edit.
\newcommand{\workingDate}{\textsc{2012 $|$ May $|$ 07}}

% Name and institution must preceed call to researchdiary.sty package
\newcommand{\userName}{Ben Keller}
\newcommand{\institution}{McMaster University}

% The guts and glory
\usepackage{researchdiary}

% Begin document
\begin{document}
\pagebreak
\subsection*{To Do}
\begin{bullets}
\item[\checkmark] Rewrite Chris' density profile code to generate SPH ICs
\item[\checkmark] Generate Tipsy file from Chris' IC
\item[\checkmark] Add Chris' potential to gasoline
\item[\checkmark] Run Chris' Disk adiabatically
\item Run Chris' Disk with fabiogal parameter
\item[\checkmark] Run violent shocktube to compare RT Forces
\end{bullets}

\textleaf : \textit{In Progress} \qquad \checkmark : \textit{Completed}

\section*{Daily Log}
\subsection*{Monday}
Internet is down right now.  May not be able to get any work done.  If it 
doesn't come back up, I will just catch up on some papers. I moved 
the things for working with Chris' Disk slice from \verb!Research/code/chris_IC!
to\verb!Research/data/chris_IC!.

The internet is restored!  I've started running (locally, on fox2) Chris' IC to
see if I can make it through one full timestep before I blast it off to run on
orca.  It crashed the first time because of a \verb!assert(bInBox)! failure,
which I believe is because the x and y range is $(0,1)$ instead of $(-0.5,0.5$.
I have fixed this in the tipsy file, and if it solves the problem, I will add 
it to \verb!mktipsy.py!.  It worked!

Running Chris' IC on orca keeps crashing with the following assertion 
violation:
\verb!pst.c:1177: _pstRootSplit: Assertion `fmm - pst->bnd.fMin[dBnd] >= -1e-14*fabs(fmm) && fmm <= pst->bnd.fMax[dBnd]' failed!
It failed at step 0.259014.  I am going to re-run it to see if it keeps
occuring at the same spot.  I'm also going to start a process on fox2
to see if it is an MPI-related thing.  If neither is fruitful, I will
have the wonderful job of finding out what this assertion actually 
means.
\subsection*{Tuesday}
I met with James today.  It looks like that failure is due to a particle falling
outside the boundaries (weird, I know.  I couldn't find it using \verb!examine!)
of the periodic box.  I've added a line to \verb!pkd.c! at line 4153 that 
prints out the position of the particle and the offending position causing the
assertion failure.  I'm going to set it to run on fox2, and hopefully that will
let me find the offending particles.

I've also re-ran Rory's shocktube with \verb!dAlphaConst=2.0! in the parameter
file.  This is used to correct for a modification flag in the artificial 
viscosity that is halving the value from what it should be (1).
\subsection*{Thursday}
Today was very productive. I met with James, and fixed Chris' IC.  James 
mentioned to me that if I use periodic boundary conditions, I shouldn't have 
the z-axis non-periodic.  It's all or nothing.  I've updated that in the param
file.  I've also found the cause of the \verb!bInBox! and \verb!fmm! assertion
failures.  My $dt$ is \textit{way} too large:  on the order of one dynamical
time.  I need it to be a tenth or a hundredth of this (the dynamical time
of Chris' IC is $\approx 10 Myr$).  What was happening was that the occasional
particle was traversing the entire length of the box \textit{twice}.  The 
periodic boundary code only wrapped the particle position once, so it still
ended up outside the box.  These smaller timesteps also run much faster, since
way smaller rungs are used.

James said in a email long ago that $10^5$ particles per CPU is the ideal run 
state for gasoline.  I'd like to run a rough benchmark to see if this is true.
I'm going to benchmark Chris' IC in \verb!Research/data/gasoline_benchmark/!.
\end{document}
