%%% Research Diary - Entry
\documentclass[11pt,letterpaper]{article}

% Working date: The date this entry is describing. Not necessary the date of last edit.
\newcommand{\workingDate}{\textsc{2011 $|$ Oct $|$ 17}}

% Name and institution must preceed call to researchdiary.sty package
\newcommand{\userName}{Ben Keller}
\newcommand{\institution}{McMaster University}

% The guts and glory
\usepackage{researchdiary}

% Begin document
\begin{document}

\subsection*{To Do}
\begin{bullets}
\item[\checkmark] Set up LaTeX log template
\item[\textleaf] Catch up on ridiculous arXiv backlog
\item[\checkmark] Run all the default examples in ChaNGa
\item[\checkmark] Read ChaNGa Documentation
\item See where to start with gasoline
\end{bullets}

\textleaf : \textit{In Progress} \qquad \checkmark : \textit{Completed}

\section*{Daily Log}
\subsection*{Wednesday}
So, before I can do any real research, I need to know how these tools work.  
James wants me to play around with an example from Tom Quinn using ChaNGa and
gasoline.  Gasoline is on imp, ChaNGa is public.  However, Tom has made some 
significant changes to it, so I need to get a copy of his version.  I've emailed
him requesting access, but no response yet.  I set up spideroak today to keep
a synced up copy of my research stuff across multiple machines.  I would've 
preferred git or a real VCS, but the setup time was practically nil, so learning
git inside and out will have to wait.
\subsection*{Thursday}
Finally got a reply from Tom Quinn, but it looks like it will still be a few 
days (weeks?) before I can get his copy of ChaNGa.  I need a UW NetID, and I
have to mail or fax(!) them a long form with my driver's license to get a login
to get in his git repo.  What a waste of my time.  So, I'm going to focus on 
working with what I have, this afternoon I will take a look at the ChaNGa 
documentation, and start looking at gasoline.  These delays are maddening, I
feel a bit like I am drowning in a backlog right now.  I've downloaded the git
versions of ChaNGa into \verb!Research/code/changa_git!  Charm is at 
\verb!Research/code/charm_git!.\\
Built charm using the interactive build script.
Compile ran successfully.  Ran the charm++ simplearrayhello successfully.  James
mentioned a Woodrow/Djezanski (sp?) galaxy creator, I should find this.  All the
charm++ tests compile successfully!  The charm++ megatest ran successfully!  For
compiling ChaNGa, you MUST point the \verb!$CHARM_DIR! environment variable at
the top of the charm source, not the compiled directory.  It looks like ChaNGa
compiled successfully!  ChaNGa teststep ran successfully.  I can't run testcosmo
without IDL, skipping that test.  ChaNGa testshock ran successfully.  I need to 
get tipsy to run testcollapse, and I needed it anyway.  Tipsy installed, needed
the following packages: \verb!xserver-xorg-dev!, \verb!libxt-dev!, 
\verb!libxaw7-dev!, \verb!libncurses5-dev!.  Make sure they are installed before
you run \verb!./configure!.  Fixed a bug in ChaNGa's ParallelGravity.cpp 
preventing it from reading the director parameters in properly: 
replace \verb!FILE *fp = fopen(param.achOutName, "r" );! with 
\verb!FILE *fp = fopen(achFile, "r" );!.  Movie creator is SLOWWWWW, but I'm
only running on one core, so it's my own damn fault.  This will take longer than
I have today, I will run it at home (MORE POWER!).  Once home, I recompiled
charm++ using the multicore-linux64 to stop using TCP/IP (probably faster).  
I've set up the movie demo to run overnight, it should be ready to view in the 
morning.
\subsection*{Friday}
The movie finished, it looks like crap (what do you expect with the settings 
used though).  Will have to write a script to turn these PPM files into a movie.

\section*{ChaNGa Documentation Notes}
ChaNGa documentation wiki is at 
http://librarian.phys.washington.edu/astro/index.php/Research:ChaNGa
\begin{bullets}
\item Tipsy file format (should find out more about this)
\item Simulates gravity using Barnes-Hut tree, $O(n\log n)$ for $n$ particles
\item Timesteps run with leapfrog integration
\end{bullets}

\end{document}
