%%% Research Diary - Entry
\documentclass[11pt,letterpaper]{article}

% Working date: The date this entry is describing. Not necessary the date of last edit.
\newcommand{\workingDate}{\textsc{2011 $|$ Nov $|$ 28}}

% Name and institution must preceed call to researchdiary.sty package
\newcommand{\userName}{Ben Keller}
\newcommand{\institution}{McMaster University}

% The guts and glory
\usepackage{researchdiary}

% Begin document
\begin{document}

\subsection*{To Do}
\begin{bullets}
\item[\checkmark] See where to start with gasoline
\item[\textleaf] Run Tom's ICs on gasoline.
\item Track down cause of ChaNGa crash at time \~0.3
\item Familiarize myself with tipsy
\end{bullets}

\textleaf : \textit{In Progress} \qquad \checkmark : \textit{Completed}

\section*{Daily Log}
\subsection*{Monday}
Over the weekend, ChaNGa running on angband crashed twice, once at time 0.34 
and then at time 0.32. I must find out the source of this if I am to get it to 
run on any machine, let alone SHARCNet.  

\subsection*{Tuesday}
I dumped the last few lines of the ChaNGa output into a textfile stored in
\verb!Research/code/changa_uw/crashlog!. I will go about analyzing it once I 
have finished getting gasoline running. I wonder if the reason it is dying 
around the same time, due to a crash in the starform.C section of the program
is that starformation "kicks in" around time 0.3?  I will have to examine this
tomorrow once gasoline is running on SHARCNet.\\

James' up-to date version of gasoline 
is stored on imp at \verb!~wadsley/pkdgrav/pkdgrav!.  I've made a copy into my 
research code directory at \verb!Research/code/gasoline!.  I will now try and 
get it to compile and run on fox2.  It looks like the \verb!Makefile! in 
gasoline is just manually edited in order to configure and compile gasoline.
There is a script called \verb!build!, but it looks old and out of date. I am 
going to try and document the compile time options for gasoline, as I need to 
know what they all are.  Thedefault option for the Makefile asks for which 
parallelization toolkit to use, I think I ought to use pthread for running on 
fox2 and angband.  Gasoline depends on \verb!mdl! from 
\verb!~wadsley/pkdgrav/mdl! on imp, so I fetched that and put it in 
\verb!Research/code/mdl!. A straight make with \verb!-DCOOLING_COSMO! fails, so
I'm trying with \verb!-DNOCOOLING!.  It failed again, but I just needed to 
recompile \verb!Research/code/mdl/pthread/mdl.o! for my CPU arch.  This compiles
the code.  Trying to run it on Tom's ICs fails, it complains of needing 
\verb!libimf.so!, but it looks like I just compiled it incorrectly.  I'm now 
trying to compile just the \verb!gasoline! executable.  Compilation of 
\verb!smoothfcn.c! fails.  I need to remove the \verb!-DNOCOOLING! flag to fix 
this.  Fixing the cooling flags allowed it to compile properly.  The option for
changing the number of threads is \verb!-sz!. I have started to run gasoline on
angband using Tom's IC.
\subsection*{Wednesday}
It looks like gasoline crashed on angband at some point last night, but I 
massively overloaded the system with handbrake as well as a 5 thread gasoline
run, so I restarted it in hopes that it was just a system resources issue.
It crashed again.  Once I get it running on SHARCNet, I will dig in to find 
the source of the crash.\\

Gasoline runs fine on SHARCNet's orca, when compile with the \verb!make mpi!
command.  Just run it using \verb!sqsub -q mpi -n NCORES ./gasoline PARAM! for
\verb!NCORES! cpus and using the parameter file \verb!PARAM!.
I found the source of the crash.  In gasoline's \verb!smooth.c! line 376, there
is an \verb!assert(0)! statement that will ALWAYS cause a crash (because assert
causes a failure if the argument is 0), unless \verb!iSmoothType! is one of the 
types in the long switch statement starting at line 36.  In other words, the 
thing crashes because I'm possibly missing a compile-time flag.  I've added
a line before line 376 to print the value of this flag, and see what is up.
That should let me know what compiler flag I need to include in order to get
the thing to run. The smoothing type that is causing crash is 2.  This 
corresponds to a \verb!smx_smoothtype! of \verb!SMX_DENSITYTMP! as defined in 
the header file \verb!smoothfcn.h!.  There actually is no flag to allow this
to be checked for in the switch!  The only flag I can see near the problem 
lines in \verb!main.c! is \verb!DENSITYU!, so I will try that.  This is a bit
of a shot in the dark!  Well, that failed.  I will remove that flag, and try
introducing into \verb!smooth.c! a fopy of the \verb!SMX_DENSITY! switch case,
modified to work with \verb!SMX_DENSITYTMP!.  Hopefully this is the appropriate
course of action, I will need to ask James about it if this works.
\subsection*{Thursday}
It turns out all of the difficulty I have had with the was because I was using
the wrong version of gasoline.  James pointed me to 
\verb!~wadsley/pkdgrav/pkdgrav_stable!, which is the right and proper version
of gasoline.  It is now running successfully on orca.
\subsection*{Friday}
My runs of gasoline on orca keep crashing.  It doesn't look like gasoline is to
blame, but flakiness on orca (infiniband crash, mpi stuff, etc.).  If I can't 
get a successful run finished by Monday, I'll have to ask James about it.  I've
been restarting them as I catch them.\\

I've started working on the manual for gasoline, I'm hoping to at least get a 
rough table of contents.
\subsection*{Saturday}
Gasoline has hung again, with no indication as to why.  I hypothesized in bed 
last night that it may be due to one or more nodes running out of memory, so
I've specified the memory per process to be 2GB rather than the default 1GB.
We shall see if that fixes things.
\section*{Edits to gasoline Makefile}
\begin{itemize}
\item Changed \verb!CC = icc! to \verb!CC = gcc!
\item Removed the line \verb!COOLING_OBJ = !
\item Removed the line \verb!COOLING_DEF = -DNOCOOLING!
\item Added the line \verb!COOLING_OBJ = cooling_cosmo.o!
\item Added the line \verb!COOLING_DEF = -DCOOLING_METAL!
\end{itemize}
\end{document}
