%%% Research Diary - Entry
\documentclass[11pt,letterpaper]{article}

% Working date: The date this entry is describing. Not necessary the date of last edit.
\newcommand{\workingDate}{\textsc{2012 $|$ Jan $|$ 23}}

% Name and institution must preceed call to researchdiary.sty package
\newcommand{\userName}{Ben Keller}
\newcommand{\institution}{McMaster University}

% The guts and glory
\usepackage{researchdiary}

% Begin document
\begin{document}

\subsection*{To Do}
\begin{bullets}
\item[\textleaf] Replicate figure 5 from Hopkins 2011
\item Track down cause of ChaNGa crash at time \~0.3
\end{bullets}

\textleaf : \textit{In Progress} \qquad \checkmark : \textit{Completed}

\section*{Daily Log}
\subsection*{Wednesday}
I have come to the unfortunate realization that gasoline's checkpointing behaves
poorly with the \verb!.log! and \verb!.starlog! files, as in it just gives up
writing to them if there is a file already there.  Ugh.  So, all of my "resumed"
jobs are lacking starformation history files.  I have restarted Tom's ICs for
the non-ionized part, because the starlog was broken.  It looks like gasoline is
\textit{supposed} to resume things gracefully, but I guess something on orca
crapped out again.  This is particulary weird, because g1536 has restarted fine
a number of times. So the status with my current simulations are:
\begin{description}
\item{\verb!/work/kellerbw/g1536_noionize_DRTFORCE!}\\ Still running, iRung is
going crazy again though
\item{\verb!/work/kellerbw/g1536_ionize_DRTFORCE!}\\ Still running, iRung
is going crazy again though
\item{\verb!/work/kellerbw/isol_galaxy_ionization_DRTFORCE!\checkmark}\\ 
Finished, copied to fox2, but the starformation rate is so low (or resolution 
is too coarse) to see any big difference in the SFR without ionization
\item{\verb!/work/kellerbw/isol_galaxy_noionization_DRTFORCE!\checkmark}\\ See
above 
\item{\verb!/work/kellerbw/Tom_IC_ionization_DRTFORCE!\checkmark}\\ Looks good,
needs to run longer.  I've set it up for 400 steps, instead of the previous 150.
\item{\verb!/work/kellerbw/Tom_IC_noionization_DRTFORCE!}\\ The log and starlog
are totally wrecked.  I've restarted from the beginning, but orca is being 
difficult today, so it may take a while
\end{description}
James suggested examining a density versus temperature phase diagram as a way 
of comparing runs.
\end{document}
